Synthesizing Quotient Lenses

### 2018-03-09 papers/QuotientLenses/main.tex
Checkpoint comment

\item The remaining eight benchmarks were derived from datasets found at 
  data.gov. These datasets include census
  population data, wage comparison data, demographics statistics data and
  crime index data. We chose these datasets since they were stored in XML, CSV
  and RDF formats which are more easily specified using regular expressions than
  plain text or PDF documents.  \bcp{Why did we include these eight new
    ones?  Are they significantly different (more complex, exercising
    different features of the synthesis algorithm or QRE syntax, ...)?}
\end{enumerate}

@@

The pre-QRE version of Optician was only able to synthesize fully bijective data
transformations.  Synthesizing from QREs loosens that restriction, making it
possible to synthesize data which is bijective when put in canonical form. To
determine the increase of expressivity, we analyzed:
\begin{enumerate}
  \item How many data formats in Optician's benchmark suite required modifications
  to be bijective.
  \item How many data formats in Optician's benchmark suite required modifications
  to be bijective when put in canonical form.
\end{enumerate}

We found that 10 of Optician's 39 benchmarks required modifications to be
bijective. We found that 4 of Optician's 39 benchmarks required modifications to
be in bijective correspondence when in canonical form.\saz{Is this somehow where
  the 14 = 10+4 points in Fig. 10 come from?}\saz{Do these 10 and 4 intersect?}
Furthermore, we found that all eight of the data.gov examples required no
modifications to be in bijective correspondence when in canonical form. While we
did not put the data.gov examples into a form suitable for pre-QRE Optician, we
found that only four of the eight data.gov examples did not require
canonization, so making them suitable for pre-QRE Optician would have required 
changes to of four of the data.gov formats.  Here again, we see that QREs add
significant expressive power.

@@

\begin{figure}[t]
\centering
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{generated-graphs/times_opt}
\caption{}
\label{subfig:lenssize}
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}
\includegraphics{generated-graphs/times_new.eps}
\caption{}
\label{subfig:examplesused}
\end{subfigure}
\caption{Runtimes of Optician and our system.
In (a), we run Optician and our system on Optician's benchmarks.  We find that
there is only a negligible difference incurred by Optometrist's overhead.
In (b), we run Optometrist on its benchmark suite.  We find that it is able
to synthesize all quotient lenses in under 20 seconds, and typically
finished in under 5 seconds. \bcp{The left-hand graph, especially, is hard
  to make anything out of, because the curves are squished against the
  axes.  Not sure what to do about this.  Also, I'm finding the terms
  ``Optician'' and ``Optometrist'' really hard to keep straight---in part
  because, in English, they are almost synonyms.}}
\label{fig:times}
\end{figure}

To assess the performance impact of adding QRE support to Optician, we measured
the running time of the following configurations:
\begin{itemize}
  \item[\OpticianRuntime{}] pre-QRE Optician running on its own benchmarks.
  \item[\SystemOnOptician{}] Optician with QREs running on the pre-QRE benchmarks.
  \item[\SystemOnBenchmarks{}] Optician with QREs running on its own benchmarks.
\end{itemize}

@@

Also notable is one of the data.gov examples, which converts demographic
statistics by zip code from xml form into rdf form. This took longer because it
was an exceptionally large format, converting over 40 fields.\saz{We need to
  explain more detail here.  I guess this is about the last benchmark in Fig. 11
  (b), which takes a long time?}  We added in additional fields to make this
format suitable for Optician, which took over 15 seconds synthesize the modified
lens.\saz{This needs more context, explanation.}

>>>>

\item The remaining eight benchmarks were derived from datasets found at 
  data.gov. These datasets include census
  population data, wage comparison data, demographics statistics data and
  crime index data. We chose these datasets since they were stored in XML, CSV
  and RDF formats which are more easily specified using regular expressions than
  plain text or PDF documents.  \BCP{Besides differing formats, why did we
    include these eight new 
    ones?  Are they significantly different (more complex, exercising
    different features of the synthesis algorithm or QRE syntax, ...)?}
\end{enumerate}

@@

The pre-QRE version of Optician was only able to synthesize fully bijective data
transformations.  Synthesizing from QREs loosens that restriction, making it
possible to synthesize data which is bijective when put in canonical
form\bcp{No: We do not synthesize data, nor is the data itself bijective.}. To
determine the increase of expressivity, we analyzed:
\begin{enumerate}
  \item How many data formats in Optician's benchmark suite required modifications
  to be bijective.
  \item How many data formats in Optician's benchmark suite required modifications
  to be bijective when put in canonical form.  \bcp{I don't understand the
    difference between these.}
\end{enumerate}

We found that 10 of Optician's 39 benchmarks required modifications to be
bijective. We found that 4 of Optician's 39 benchmarks required modifications to
be in bijective correspondence when in canonical form.\saz{Is this somehow where
  the 14 = 10+4 points in Fig. 10 come from?}\saz{Do these 10 and 4 intersect?}
Furthermore, we found that all eight of the data.gov examples required no
modifications to be in bijective correspondence when in canonical
form.\BCP{Is this surprising?  We could have chosen the examples so that
  this is true.} While we
did not put the data.gov examples into a form suitable for pre-QRE
Optician\bcp{What does that mean?}, we
found that only four of the eight data.gov examples did not require
canonization, so making them suitable for pre-QRE Optician would have required 
changes to of four of the data.gov formats.  Here again, we see that QREs add
significant expressive power.

@@

\begin{figure}[t]
\centering
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{generated-graphs/times_opt}
\caption{}
\label{subfig:lenssize}
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}
\includegraphics{generated-graphs/times_new.eps}
\caption{}
\label{subfig:examplesused}
\end{subfigure}
\caption{Runtimes of Optician and our system.
In (a), we run Optician and our system on Optician's benchmarks.  We find that
there is only a negligible difference incurred by Optometrist's overhead.
In (b), we run Optometrist on its benchmark suite.  We find that it is able
to synthesize all quotient lenses in under 20 seconds, and typically
finished in under 5 seconds. \bcp{The left-hand graph, especially, is hard
  to make anything out of, because the curves are squished against the
  axes and have almost identical shapes.  Not sure what to do about this.
  Also, I'm finding the terms 
  ``Optician'' and ``Optometrist'' really hard to keep straight---in part
  because, in English, they are almost synonyms.}}
\label{fig:times}
\end{figure}

To assess the performance impact of adding QRE support to Optician, we measured
the running time of the following configurations:
\begin{itemize}
  \item[\OpticianRuntime{}] pre-QRE Optician running on its own benchmarks.
  \item[\SystemOnOptician{}] Optician with QREs running on the pre-QRE benchmarks.
  \item[\SystemOnBenchmarks{}] Optician with QREs running on its own
  benchmarks. \BCP{What is the difference between QO and QQ??  The eight
    additional benchmarks?  Why not measure just these?  Seems like this
    graphj repeats some information from the one to the left, obscuring the
    new information.}
\end{itemize}

@@

Also notable is one of the data.gov examples, which converts demographic
statistics by zip code from xml form into rdf form. This took longer because it
was an exceptionally large format, converting over 40 fields.\saz{We need to
  explain more detail here.  I guess this is about the last benchmark in Fig. 11
  (b), which takes a long time?\bcp{It's a bit hidden in the figure...}}  We
added in additional fields to make this 
format suitable for Optician, which took over 15 seconds synthesize the modified
lens.\saz{This needs more context, explanation.}
